%-------------------------
% LaTeX Resume
% Author : Gabriel Ong
% Website: https://www.overleaf.com/project
% License : MIT
%------------------------

% -------------- Dependencies ---------------

\documentclass[11pt, letterpaper]{article}

\usepackage[left=0.5in,top=0.4in,right=0.5in,bottom=0.4in]{geometry} 
\usepackage[parfill]{parskip} 

\usepackage{etoolbox}
\usepackage{keycommand}
\usepackage{xstring}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=black,
}

\usepackage[scaled]{helvet} 
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc} 
\pagestyle{empty}

% ------------ Utilities ------------

\def \separator {
    \textbf{\Large\textbullet}
}

\newcommand{\email}[1]{\href{mailto:#1}{#1}}%
\newcommand{\profilelink}[1]{\href{https://#1}{#1}}%

\newcommand{\isA}[1]{
    \expandafter\ifstrequal\expandafter{#1}{default}{}{a}
}

\newcommand\sectionTitle[1]{%
    \begingroup
        \textbf{\MakeUppercase{#1}}
        \vspace{0.4em}
        \hrule
        \vspace{-0.3em}
    \endgroup
}%

% ------------- Header Template --------------

\newcommand\printNameDesc[7]{%
    \begingroup
        \begin{minipage}[t]{0.6\textwidth} 
            {\raggedright\huge\bfseries #1\par} 
            \vspace{0.3em} 
            {\raggedright\Large \href{https://#3}{#3}\par}
            \vspace{0.4em} 
            {\raggedright #2\par} 
        \end{minipage}%
        \begin{minipage}[t]{0.4\textwidth} 
            \raggedleft 
            #4 \par
            \href{mailto:#5}{#5} \par
            \href{https://#7}{#7} \par
            \href{https://#6}{#6}
        \end{minipage}
        \vspace{0.5em}
    \endgroup
}

\newkeycommand{\introduction}[
    fullname,
    description,
    website,
    email,
    phone,
    github,
    linkedin,
]{%
    \printNameDesc{\commandkey{fullname}}{\commandkey{description}}{\commandkey{website}}{\commandkey{phone}}{\commandkey{email}}{\commandkey{github}}{\commandkey{linkedin}}
}

% ------------ Education Template ------------

\newenvironment{educationSection}[1]{%
    \sectionTitle{#1}%
}%

\newkeycommand{\educationItem}[
    school,
    program,
    period,
    grade
]{%
    \textbf{\commandkey{school}} \hfill \commandkey{period} \\ 
    \commandkey{program} \hfill \raggedleft\commandkey{grade} %
}

% -------------- Skills Template --------------

\newenvironment{skillsSection}[1]{%
    \sectionTitle{#1}%
}%

\newkeycommand{\skillItem}[
    category,
    skills
]{%
    {%
        \bf \commandkey{category}:
    } {%
        \commandkey{skills}%
    }
}%

% -------------- Experience Template -------------

\newenvironment{experienceSection}[1]{%
    \sectionTitle{#1}%
    \begin{list}{}{ % List for each highlight in the section
        \setlength{\leftmargin}{0em} % Margin within the section
    }%
        \item[]%
    }{%
    \end{list}%
}%

\newkeycommand{\experienceItem}[
    company,
    position,
    location,
    duration
]{%
    \textbf{%
        \commandkey{company},
        \commandkey{location}:
        \it{\commandkey{position}}
    } \hfill {%
        \commandkey{duration}%
    }
    \vspace{-0.5em}%
}%

% ----------------- Project Template -------------

\newenvironment{projectSection}[1]{%
    \sectionTitle{#1}%
}%

\newkeycommand{\projectItem}[
    name,
    summary,
    url
]{%
    {%
        \bfseries
        \href{\commandkey{url}}{\commandkey{name}}:
    } {%
        \commandkey{summary}%
    }
}

% ----------------- Awards and Competitions Template -------------

\newenvironment{awardCompetitionSection}[1]{%
    \sectionTitle{#1}%
}%

\newkeycommand{\awardCompetitionItem}[
    name,
    organisation,
    period,
]{%
    \textbf{\commandkey{name}} \hfill \commandkey{period} \\ 
    \commandkey{organisation}%
}

% ----------------------------------------

% ---------------- Resume ----------------

% ----------------------------------------

\begin{document}

% --------- Contact Information -----------
\introduction[
    fullname={Gabriel Ong Zhe Mian},
    description={Full-Stack Developer specialising in Legal Technology},
    website={gabrielongzm.com},
    email={gabrielzmong@gmail.com},
    phone={+65-8123-9863},
    github={github.com/gongahkia},
    linkedin={linkedin.com/in/gabriel-zmong}
]

% --------- Education ---------

\begin{educationSection}{Education}

    \educationItem[
        school={Singapore Management University},
        program={BSc Computing and Law, Cybersecurity (2nd Major)},
        period={Aug. 2023 - May 2027},
        grade={GPA: 3.60/4.00}
    ]

    \educationItem[
        school={Anglo-Chinese School (Independent)},
        program={International Baccalaureate Diploma Programme},
        period={Jan. 2019 - Nov. 2020},
        grade={Points: 44/45}
    ]
    
\end{educationSection}

% --------- Skills -----------

\begin{skillsSection}{Skills}

    \skillItem[
        category={Frontend},
        skills={React, Next.js, React Native, Flutter, Electron.js}
    ] \\
    \skillItem[
        category={Backend},
        skills={Python, TypeScript, Go, Rust, SQL, Java, Node.js}
    ] \\
    \skillItem[
        category={Cloud},
        skills={GCP, AWS, Docker, Kubernetes, GitHub Actions, Supabase, MongoDB, Pinecone, Cloudflare}
    ] \\
    \skillItem[
        category={Legal},
        skills={Intellectual Property Law, Privacy \& Data Protection Law, Company Law, Contract Law}
    ]

\end{skillsSection}

% --------- Experience -----------

\begin{experienceSection}{Experience}

    \experienceItem[
        company={WhyHow.AI},
        location={San Francisco},
        position={Software Development Intern},
        duration={Aug. 2025 - Dec. 2025}
    ]
    \begin{itemize}
        \setlength{\itemsep}{-6pt}
        \item Architected a multi-agent ETL pipeline using \textbf{Python} and \textbf{Pydantic AI} to detect emergent harms across 10,000+ PubMed abstracts, reducing manual review time by an estimated \textbf{60\%}.
    \end{itemize}

    \experienceItem[
        company={Custom Automated Systems},
        location={Singapore},
        position={Full-Stack Development Intern},
        duration={May 2025 - Aug. 2025}
    ]
    \begin{itemize}
        \setlength{\itemsep}{-6pt}
        \item Implemented RAG and Agentic Refinement in \textbf{TypeScript} with \textbf{Hugging Face} models on ProQuaere's Outputs. 
        \item Optimised client-side LLM inference for ProQuaere across browser, desktop, and mobile platforms using \textbf{WebGPU} and \textbf{Electron.js}, achieving a \textbf{40\%} reduction in average response latency.
        \item Upgraded Caselist's \textbf{PHP} Backend for Legal Case Retrieval from CommonLII, Lawphil, SAL LawNet Databases. 
    \end{itemize}

    \experienceItem[
        company={SMU Yong Pung How School of Law},
        location={Singapore},
        position={Research Assistant},
        duration={Jan. 2025 - Aug. 2025}
    ]
    \begin{itemize}
        \setlength{\itemsep}{-6pt}
        \item Built a collection of Adversarial AI agents with \textbf{Pydantic AI} and \textbf{ChromaDB} for use in legal scholarship and argumentation.
        \item Developed and deployed a \textbf{JavaScript} web application enabling researchers to benchmark adversarial AI agents across standardized legal analysis tasks, supporting ongoing academic publication research.
    \end{itemize}

    \experienceItem[
        company={Elefant},
        location={Singapore},
        position={Backend Development Intern},
        duration={Sep. 2024 - Dec. 2024}
    ]
    \begin{itemize}
        \setlength{\itemsep}{-6pt}
        \item Engineered \textbf{CI/CD} pipelines in \textbf{Python} that automated end-to-end data extraction, enrichment, and validation workflows, reducing manual data processing effort by \textbf{65\%} and improving data reliability.
        \item Deployed web monitoring solutions in \textbf{GCP} to log continuous data availability. 
    \end{itemize}

    \experienceItem[
        company={SMU Legal Innovation and Technology (LIT)},
        location={Singapore},
        position={Tech Development Director},
        duration={Aug. 2023 - Aug. 2024}
    ]
    \begin{itemize}
        \setlength{\itemsep}{-6pt}
        \item Led development of 3 open-source legal tech tools in \textbf{Python}, \textbf{JavaScript}, and \textbf{Rust} as Tech Development Director, growing the club's GitHub presence and onboarding \textbf{10+} student contributors.
    \end{itemize}

\end{experienceSection}

% --------- Projects -----------

\begin{projectSection}{Projects}

    \projectItem[
        name={Yuho},
        summary={Domain-specific language (DSL) in \textbf{Rust} that provides a formal, programmatic representation of Singapore's Penal Code, enabling automated legal reasoning and statute querying across \textbf{50+} criminal offences.},
        url={https://github.com/gongahkia/yuho}
    ] \\
    \projectItem[
        name={Sea Kayak},
        summary={Full-stack \textbf{React} and \textbf{Node.js} web application that aggregates and curates real-time legal news from \textbf{10+} Singapore sources.},
        url={https://github.com/gongahkia/sea-kayak}
    ] \\
     \projectItem[
        name={Jikai},
        summary={Tort law hypothetical generation system using \textbf{RAG} and multi-agent pipelines in \textbf{Python}, \textbf{ChromaDB} and \textbf{LangChain}, enabling law students and researchers to generate and stress-test novel legal scenarios for academic study.},
        url={https://github.com/gongahkia/jikai}
    ]   

\end{projectSection}

% --------- Awards -----------

\begin{awardCompetitionSection}{Awards \& Competitions}

    \awardCompetitionItem[
        name={SMU Global Impact Scholarship Award},
        organisation={Premier flagship scholars’ award},
        period={Aug. 2023 - May 2027}
    ]

    \awardCompetitionItem[
        name={SMU LIT Hackathon 2025},
        organisation={1st Place (MinLaw Track 2)},
        period={Sep. 2025}
    ]

    \awardCompetitionItem[
        name={NUS Product Club Vibe-Building Hackathon 2025},
        organisation={2nd Place},
        period={Aug. 2025}
    ]

    \awardCompetitionItem[
        name={HackOMania 2025},
        organisation={GeeksHacking Choice Award},
        period={Feb. 2025}
    ]

    \awardCompetitionItem[
        name={YouthTechSG YouthxHack 2024},
        organisation={1st Place (Digital Defence Track)},
        period={Aug. 2024}
    ]

\end{awardCompetitionSection}

\end{document}

% --------------------------------------
